Fiber Collision Correction Method for BOSS Power Spectrum

### 2015-03-24 qfenv_paper/ApJ submission/referee_response.txt

        N_{env}. Can this have a value between 0 and 1? I would have thought
        all the weights would be >=1. Therefore better to state the low-density
        environment as n_{env} = 0.

No, n_{env} cannot have a value between 0 and 1. We have corrected the
low-density environment cut-off to n_{env} = 0 throughout the text and in all
the figures.

        Section 2.6: Why does this need to use random points? Why not a finely
        spaced regular grid in RA and DEC?

We use random points due to the convenience of the ransack commands, which
generates random points given a survey geometry. We believe that the referee's
suggestion of a finely spaced regular grid would not make a significant
difference in accounting for the edge effects.

@@

Corrected.

        Page 12 and elsewhere: The caveat that PRIMUS has more galaxies, and
        therefore better statistics than zCOSMOS is that the environmental
        measures are possibly significantly less reliable because of redshift
        uncertainties. I think this should be pointed out a couple of more
        times than is done currently within the text. There is also the issue
        of overall redshift completeness (targeting and redshift success
        combined), how does PRIMUS compare with zCOSMOS in this regard?

We now explicitly state, in Section 4.3, that our galaxy environment measures
are susceptible to contamination due to PRIMUS redshift uncertainties. We also
emphasize the role of the redshift uncertainties in motivating the more
stringent high density environment classifications in Section 4.2.

As suggested by the referee, we also discuss the overall redshift completeness
of PRIMUS versus zCOSMOS in Section 4.3.

### 2015-03-24 fc_paper/fc_paper.tex
Abstract written

\begin{abstract}
Redshift surveys, including BOSS, use fiber fed spectrographs. A fiber is used for each galaxy in order obtain its redshift. However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information. In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated. Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.
\end{abstract}
\keywords{cosmology: observations --- }

\section{Introduction} 
\begin{itemize}
\item fiber-fed multi-object spectroscopic surveys allow us to collect large redshift data, which is why it?s the favorite of cosmology surveys
\item moving from statistics dominated regime to systematics dominated regime
\end{itemize}

Redshift surveys, including BOSS, use fiber fed spectrographs. A fiber is used for each galaxy in order obtain its redshift. However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information. In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated. Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.

@@

In the following sections, we present our fiber-collision correction results using a series of simulations. Ultimately, we apply our correction to the BOSS data. 
% Include cosmology assumption and out line of paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collided Mock Catalogues
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
For various purposes such as calculating the covariance matrix or estimating cosmic variance, simulated mock catalogues play a crucial role in measuring clustering statistics of observed galaxy data (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber-collisions (CITE CITE). By using mock catalogues, we can test how these effects influence clustering results and devise correction methods that attempt to account for these effects.

@@

Finally in the right panel (Tiling Mock), we find that $\chi^2(k_\mathrm{max})$ increases in a near monotonic fashion as a function of $k_\mathrm{max}$. For $k_\mathrm{max} < 4\times10^{-2} \; h/\mathrm{Mpc}$, there are no significant differences between the $\chi^2$s of all the correction methods. Then from $4\times10^{-2} < k_\mathrm{max} < 1.5\times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2$s of NN-upweight and \cite{Beutelr:2014aa} are notably lower than the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method. However at smaller scales, the $\chi^2$s of NN-upweight and \cite{Beutelr:2014aa} quickly rise beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$. In the meantime, $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.32$ for \cite{Gil-Marin:2014aa} and $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.15$ for our correction method. Moreover, through the entire $k_\mathrm{max}$ our method has a lower $\chi^2$ than \cite{Gil-Marin:2014aa}. With only one realization of the Tiling Mocks and scaled $\Delta P$, a detailed comparison of the $\chi^2$ values is impossible. Yet the $\chi^2(k_\mathrm{max})$ results for our correction provide realistic assurance that the correction method can be applied to the actually BOSS data.

>>>>

\begin{abstract}
With their ability to collect large amounts of redshift data, fiber-fed multi-object spectroscopic surveys dominate cosmological studies. However, the physical size of the fibers limit the ability of these surveys from successfully collecting redshifts from galaxies within the fiber-collision angular scale. These fiber-collisions ultimately leads to systematic effects on galaxy clustering measurements. Using simulated mock catalogues already extensively used in interpreting large-scale structure clustering measurements of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the power spectrum in particular. We compare current fiber-collision correction methods in the literature and assess their success in reconstructing the true power spectrum for the mock catalogues. We then present our fiber-collision correction method. Our method uses the distribution of the line-of-sight displacements between resolved fiber-collided pairs in order to statistically reconstruct clustering on small scales along with a proper accounting of fiber-collisions in the shot-noise correction term of the power spectrum estimator. Using our method, we reproduce the true power spectrum for the mock catalogues with residuals of $\sim 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$. Finally, comparison to other fiber-collision correction methods reveal that the method better reproduces the true power spectrum especially at small scales, with the added advantage that the method can be validated and calibrated in actual data. 
\end{abstract}
\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}

\section{Introduction} 
Through the tens of million redshifts obtained through redshift surveys, cosmological measurements are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements. Most of these cosmology focused redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; CITE CITE) and the Baryon Oscillation Spectroscopic Survey (BOSS; CITECITE) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) use fiber fed spectrographs. For each galaxy, a fiber is used to obtain a spectroscopic redshift. However, due to the physical size of the fibers even with efficient targeting strategies (e.g. \citealt{Blanton:2003ab} for SDSS), if galaxies are located within the fiber-collision angular scale from each other on the sky, two separate fibers cannot be placed adjacently to separately extract the spectroscopic information. In these cases, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured. Furthermore, as we probe to higher redshifts in our cosmological studies, the fiber-collision angular scale correspond to a larger comoving scale thereby affecting our measurements on larger scales.

Though this only accounts for a small fraction of the redshifts ($< 5\%$ of the BOSS redshift survey) its effect on clustering measurements such as the power spectrum is significant and must be understood as our cosmological measurements become more detailed and sophisticated.

@@

In the following sections, we present our fiber-collision correction results using a series of simulations. Ultimately, we apply our correction to the BOSS data. 
% Include cosmology assumption and out line of paper
\begin{itemize}
\item Even advancements in fiber positioners won't eliminate the fiber-collision issues in high density regions \cite{Morales:2012aa}. 
\item Fibercollision gets worse in comoving scales 
\item \cite{Zehavi:2002aa} FC in SDSS (example of the upweighting method) only works for fiber-collision scales and fails below it
\item Perhaps the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Makarem:2014aa}) will render fiber-collisions obsolete, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics. 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collided Mock Catalogues
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
For various purposes such as calculating the covariance matrix or estimating cosmic variance, simulated mock catalogues play a crucial role in measuring clustering statistics of observed galaxy data (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber-collisions (\citealt{Yoon:2008aa, Guo:2012aa} LIST MORE). By using mock catalogues, we can test how these effects influence clustering results and devise correction methods that attempt to account for these effects.

@@

Finally in the right panel (Tiling Mock), we find that $\chi^2(k_\mathrm{max})$ increases in a near monotonic fashion as a function of $k_\mathrm{max}$. For $k_\mathrm{max} < 4\times10^{-2} \; h/\mathrm{Mpc}$, there are no significant differences between the $\chi^2$s of all the correction methods. Then from $4\times10^{-2} < k_\mathrm{max} < 1.5\times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2$s of NN-upweight and \cite{Beutler:2014aa} are notably lower than the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method. However at smaller scales, the $\chi^2$s of NN-upweight and \cite{Beutler:2014aa} quickly rise beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$. In the meantime, $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.32$ for \cite{Gil-Marin:2014aa} and $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.15$ for our correction method. Moreover, through the entire $k_\mathrm{max}$ our method has a lower $\chi^2$ than \cite{Gil-Marin:2014aa}. With only one realization of the Tiling Mocks and scaled $\Delta P$, a detailed comparison of the $\chi^2$ values is impossible. Yet the $\chi^2(k_\mathrm{max})$ results for our correction provide realistic assurance that the correction method can be applied to the actually BOSS data.
